Deep Learning

### 2015-01-27 deepreview.tex
small changes on Geoff's big commit

The major factors in this
success were the large labeled dataset~\citep{imagenet_cvpr09}, the use of fast GPUs,
and the convolutional early layers.  
%% REPETITION
%% It had already been shown that deep
%% supervised nets with rectified linear units could be trained without
%% unsupervised pre-training~\citep{Glorot+al-AI-2011-small}. 
Rectified linear units made the
training much faster and the fully connected final layers were prevented
from overfitting the peculiarities of the training set by randomly omitting
hidden units during training~\citep{Srivastava14}. Deep convolutional nets
have quickly replaced the carefully engineered pipelines full of
hand-designed features developed by the computer vision community and they
are now deployed in many computer vision applications, including image
tagging, object detection, face recognition, facial expression recognition
and scene parsing.

@@

Instead of translating the meaning of a French sentence to an English sentence,
one can learn to ``translate'' the meaning of an image into an English sentence,
as illustrated in Figure~\ref{fig:caption-generation}. The ``encoder'' here is
a deep convolutional neural network which converts the pixels into an
activiy vector in its last hidden layer. The ``decoder''
is a recurrent neural network similar to the ones used for machine translation
and neural language modeling. There has been a surge of interest in such
systems recently~\citep{Kiros-et-al-ICML2014,Mao+al-arxiv2014,Donahue-et-al-arxiv2014,
              Vinyals-et-al-arxiv2014,Fang-et-al-arxiv2014,
             Chen+Zitnick-arxiv2014,Karpathy+Li-arxiv2014,Venugopalan-et-al-arxiv2014}.

\begin{figure}[ht]
\fbox{
\begin{minipage}{\textwidth}
\centerline{\includegraphics[width=\linewidth]{caption-generation-Vinyals-et-al.png}}
\centerline{\includegraphics[width=0.49\linewidth]{Examples_im2txt_001.png}
\includegraphics[width=0.49\linewidth]{Examples_im2txt_002.png}}
\caption{Three examples of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from a test image, with the recurrent network trained to ``translate''
high-level reprsentations of images into captions. GT stands for ``Ground Truth'' and was labeled by humans
whereas the other text is machine-generated.
Reproduced with permission from~\citet{Vinyals-et-al-arxiv2014}.
}
\label{fig:caption-generation}
\end{minipage}
}
\end{figure}

>>>>

The major factors in this
success were the large labeled dataset~\citep{imagenet_cvpr09}, the use of fast GPUs,
and the convolutional early layers.  
%% REPETITION : YB, actually it was not said earlier, only that ReLU was better than sigmoid or tanh
It had already been shown that deep
supervised nets with rectified linear units could be trained without
unsupervised pre-training~\citep{Glorot+al-AI-2011-small}. 
Rectified linear units made the
training much faster and the fully connected final layers were prevented
from overfitting the peculiarities of the training set by randomly omitting
hidden units during training~\citep{Srivastava14}. Deep convolutional nets
have quickly replaced the carefully engineered pipelines full of
hand-designed features developed by the computer vision community and they
are now deployed in many computer vision applications, including image
tagging, object detection, face recognition, facial expression recognition
and scene parsing.

@@

Instead of translating the meaning of a French sentence to an English sentence,
one can learn to ``translate'' the meaning of an image into an English sentence,
as illustrated in Figure~\ref{fig:caption-generation}. The ``encoder'' here is
a deep convolutional neural network which converts the pixels into an
activity vector in its last hidden layer. The ``decoder''
is a recurrent neural network similar to the ones used for machine translation
and neural language modeling. There has been a surge of interest in such
systems recently~\citep{Kiros-et-al-ICML2014,Mao+al-arxiv2014,Donahue-et-al-arxiv2014,
              Vinyals-et-al-arxiv2014,Fang-et-al-arxiv2014,
             Chen+Zitnick-arxiv2014,Karpathy+Li-arxiv2014,Venugopalan-et-al-arxiv2014}.

\begin{figure}[ht]
\fbox{
\begin{minipage}{\textwidth}
\centerline{\includegraphics[width=\linewidth]{caption-generation-Vinyals-et-al.png}}
\centerline{\includegraphics[width=0.49\linewidth]{Examples_im2txt_001.png}
\includegraphics[width=0.49\linewidth]{Examples_im2txt_002.png}}
\caption{Three examples of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from a test image, with the recurrent network trained to ``translate''
high-level representations of images into captions. GT stands for ``Ground Truth'' and was labeled by humans
whereas the other text is machine-generated.
Reproduced with permission from~\citet{Vinyals-et-al-arxiv2014}.
}
\label{fig:caption-generation}
\end{minipage}
}
\end{figure}
